Reanalysis Step 5: Outcome Analysis with Three-Way Interaction

### 2025-09-01 reanalysis-5-outcome_analysis-interaction.qmd
dont cache

  # Pool each subgroup using Rubin's rules
  for (j in 1:n_subgroups) {
    # Pool odds ratio contrasts (log scale)
    log_odds_estimates <- sapply(all_contrasts, function(x) x$estimate[j])
    log_odds_SEs <- sapply(all_contrasts, function(x) x$SE[j])

    # Apply Rubin's rules for log odds
    Q_bar_log <- mean(log_odds_estimates)
    U_bar_log <- mean(log_odds_SEs^2)
    B_log <- var(log_odds_estimates)
    T_log <- U_bar_log + (1 + 1/n_imputations) * B_log

@@

    # Pool risk differences (probability scale)
    rd_estimates <- sapply(all_risk_diffs, function(x) x$estimate[j])
    rd_SEs <- sapply(all_risk_diffs, function(x) x$SE[j])

    # Apply Rubin's rules for risk differences
    Q_bar_rd <- mean(rd_estimates)
    U_bar_rd <- mean(rd_SEs^2)
    B_rd <- var(rd_estimates)
    T_rd <- U_bar_rd + (1 + 1/n_imputations) * B_rd

>>>>

  # Check column names in first imputation for debugging
  if (length(all_contrasts) > 0) {
    message("Contrast columns: ", paste(names(all_contrasts[[1]]), collapse = ", "))
  }
  if (length(all_risk_diffs) > 0) {
    message("Risk diff columns: ", paste(names(all_risk_diffs[[1]]), collapse = ", "))
  }

  # Pool each subgroup using Rubin's rules
  for (j in 1:n_subgroups) {
    # Pool odds ratio contrasts (log scale)
    log_odds_estimates <- sapply(all_contrasts, function(x) {
      if ("estimate" %in% names(x)) {
        x$estimate[j]
      } else {
        # Try other possible column names
        x[j, which(names(x) %in% c("estimate", "emmean", "contrast"))[1]]
      }
    })

    log_odds_SEs <- sapply(all_contrasts, function(x) {
      if ("SE" %in% names(x)) {
        x$SE[j]
      } else if ("std.error" %in% names(x)) {
        x$std.error[j]
      } else {
        x[j, which(names(x) %in% c("SE", "std.error", "se"))[1]]
      }
    })

    # Convert to numeric and check for validity
    log_odds_estimates <- as.numeric(log_odds_estimates)
    log_odds_SEs <- as.numeric(log_odds_SEs)

    # Apply Rubin's rules for log odds
    Q_bar_log <- mean(log_odds_estimates, na.rm = TRUE)
    U_bar_log <- mean(log_odds_SEs^2, na.rm = TRUE)
    B_log <- var(log_odds_estimates, na.rm = TRUE)
    T_log <- U_bar_log + (1 + 1/n_imputations) * B_log

@@

    # Pool risk differences (probability scale)
    # Check for column names - emmeans may use 'estimate' or other names
    rd_estimates <- sapply(all_risk_diffs, function(x) {
      if ("estimate" %in% names(x)) {
        x$estimate[j]
      } else if ("emmean" %in% names(x)) {
        x$emmean[j]
      } else if ("prob" %in% names(x)) {
        x$prob[j]
      } else {
        # Try to get the estimate column (might be named differently)
        x[j, which(names(x) %in% c("estimate", "emmean", "prob", "prediction"))[1]]
      }
    })

    rd_SEs <- sapply(all_risk_diffs, function(x) {
      if ("SE" %in% names(x)) {
        x$SE[j]
      } else if ("std.error" %in% names(x)) {
        x$std.error[j]
      } else {
        # Try to get the SE column
        x[j, which(names(x) %in% c("SE", "std.error", "se"))[1]]
      }
    })

    # Convert to numeric and check for validity
    rd_estimates <- as.numeric(rd_estimates)
    rd_SEs <- as.numeric(rd_SEs)

    # Check if we got valid numeric values
    if (any(is.na(rd_estimates)) || any(is.na(rd_SEs))) {
      warning(paste("Missing values in risk difference pooling for subgroup", j))
    }

    # Apply Rubin's rules for risk differences
    Q_bar_rd <- mean(rd_estimates, na.rm = TRUE)
    U_bar_rd <- mean(rd_SEs^2, na.rm = TRUE)
    B_rd <- var(rd_estimates, na.rm = TRUE)
    T_rd <- U_bar_rd + (1 + 1/n_imputations) * B_rd
